### 2025-09-18 paper/sec/appendix-prompts.tex
Roll out 'agent' macros.
Corrections to Table 2.
Minor corrections.
[update] ref
[update] change path of system prompts

\VerbatimInput[fontsize=\small]{../system-prompt/system-prompt.txt}

@@

\VerbatimInput[fontsize=\small]{../recognition-agent/system-prompt.txt}

>>>>

\VerbatimInput[fontsize=\small]{../system-prompt/interpretation-agent/system-prompt.txt}

@@

\VerbatimInput[fontsize=\small]{../system-prompt/suggestion-agent/system-prompt.txt}
